### 2021-10-05 analysis/analyse_proportion_of_scouts.Rmd
started with the PCA analysis, see if it makes sense

@@

# put proportion of scouts into landuse data
urban_lu_long <- sitedata %>%
  select(site, p) %>%
  inner_join(urban_lu) %>%
  pivot_longer(!c(site, p), names_to = "landuse", values_to = "values")

rural_lu_long <- sitedata %>%
  select(site, p) %>%
  inner_join(rural_lu) %>%
  pivot_longer(!c(site, p), names_to = "landuse", values_to = "values")
```

@@

@@

urban_lu_long %>%
  ggplot(aes(x = p, y = values)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~landuse, ncol = 2) +
  theme(
    text = element_text(size = 8)
  )
```

>>>>

## Set up data and environment

@@

# put proportion of scouts into landuse data
urban_lu <- sitedata %>%
  select(site, p) %>%
  inner_join(urban_lu)

urban_lu_long <- urban_lu %>%
  pivot_longer(!c(site, p), names_to = "landuse", values_to = "values")

rural_lu <- sitedata %>%
  select(site, p) %>%
  inner_join(rural_lu)
rural_lu_long <- rural_lu %>%
  pivot_longer(!c(site, p), names_to = "landuse", values_to = "values")
```

@@

## Basic analysis

@@

urban_lu_long %>%
  ggplot(aes(x = p, y = values)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~landuse, ncol = 2) +
  theme(
    text = element_text(size = 8)
  )

```

## Princple Component Analysis

prcomp(urban_lu[, 3:length(names(urban_lu))])
```
